A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-07-02 tex/paper.tex
running just order 24

@@

\begin{deluxetable}{llrlr@{$\pm$}lr@{$\pm$}lr@{$\pm$}ll} 
\tablecaption{\label{table:tests} Tests}
\tablehead{
  \colhead{Object} & \colhead{Orders} & \colhead{$\lambda$ range [\AA]} & \colhead{library} &
  \multicolumn{2}{c}{$T_{\rm eff} \pm \sigma$} & \multicolumn{2}{c}{$\log g \pm \sigma$} &
  \multicolumn{2}{c}{$\Z \pm \sigma$} & \colhead{comments}
}
\startdata
WASP-14 & 22-24 & 5060-5315 & Kurucz &  &  &  &  &  & & No covariance\\
WASP-14 & 22-24 & 5060-5315& Kurucz & 6314 & 50 & 3.92 & 0.08 & -0.39 & 0.03 & Matern only\\
WASP-14 & 22-24 & 5060-5315& Kurucz & 6512 & 32 & \multicolumn{2}{c}{\nodata} & -0.27 & 0.02 & Matern + fixed $\log g = 4.29$\\
WASP-14 & 22-24 & 5060-5315 & PHOENIX & & & & & & & No covariance \\
WASP-14 & 22-24 & 5060-5315 & PHOENIX & & & & & & & Matern only \\
WASP-14 & 22-24 & 5060-5315 & PHOENIX & & & \multicolumn{2}{c}{\nodata} & & & Matern + fixed $\log g = 4.29$ \\
WASP-14 & 22-24 & 5060-5315 & PHOENIX & & & & & & & Regions included \\
\enddata
\end{deluxetable}

>>>>

\subsection{Fitting data}

[This may need to be eventually moved to \S2, but here it is for now] Cite papers that acquired the data. Describe the instruments. Describe when it was taken. Describe the noise properties, etc. Maybe a table might be worthwhile to describe the spectra. Here also describe the WASP-14 fit using the Kurucz spectra, using a fixed log g, and state that they are the same as Willie's paper. Talk about putting things in a Bayesian framework, using a sensitivity to a prior, to a $\delta$-function prior. Point out that this Bayesian approach allows you to do this.

\subsection{Generic Tests}

Designed to show off what the model framework can actually do.

Talk about giving more reasonable errors using regions, in the biased case.

@@

\begin{deluxetable}{llrlr@{$\pm$}lr@{$\pm$}lr@{$\pm$}ll} 
\tablecaption{\label{table:tests} Tests}
\tablehead{
  \colhead{Object} & \colhead{Orders} & \colhead{$\lambda$ range [\AA]} & \colhead{library} &
  \multicolumn{2}{c}{$T_{\rm eff} \pm \sigma$} & \multicolumn{2}{c}{$\log g \pm \sigma$} &
  \multicolumn{2}{c}{$\Z \pm \sigma$} & \colhead{comments}
}
\startdata
WASP-14 & 22-24 & 5060-5315 & Kurucz & 6310 & 52 & 3.91  & 0.08 & -0.38  & 0.03 & Poisson only\\
WASP-14 & 22-24 & 5060-5315& Kurucz & 6314 & 50 & 3.92 & 0.08 & -0.39 & 0.03 & Matern only\\
WASP-14 & 22-24 & 5060-5315& Kurucz & 6512 & 32 & \multicolumn{2}{c}{\nodata} & -0.27 & 0.02 & Matern + fixed $\log g = 4.29$\\
WASP-14 & 23 & & PHOENIX & 6021 & 16 & 3.83 & 0.3 & -0.50 & 0.01 & Poisson only \\
WASP-14 & 22-24 & 5060-5315 & PHOENIX & 6117 & 30 & 3.73 & 0.06 & -0.52 & 0.02 & Poisson only \\
WASP-14 & 22-24 & 5060-5315 & PHOENIX & 5865 & 43 & 3.2 & 0.08 & -0.85 & 0.03 & Matern only. Because of 24. \\
WASP-14 & 22-24 & 5060-5315 & PHOENIX & & & \multicolumn{2}{c}{\nodata} & & & Matern + fixed $\log g = 4.29$ \\
WASP-14 & 22-24 & 5060-5315 & PHOENIX & & & & & & & Regions included \\
\enddata
\end{deluxetable}
